# (APPENDIX) Appendix {-}

# NEWS {#booknews}

## 0.1.5

* 2019-04-22, use a darker blue for links.

* 2019-04-08, improve formatting and link text in README (@katrinleinweber, #137)

* 2019-03-25, add favicon (@wlandau, #136).

* 2019-03-21, improve Travis CI guidance, including link to examples. (@mpadge, #135)

* 2019-02-07, simplify code examples in Package Evolution section (maintenance_evolution.Rmd file) (@hadley, #129).

* 2019-02-07, added a PDF file to export.

* 2019-02-01, created a .zenodo.json to explicitely set editors as authors.

## First release 0.1.0

* 2019-01-23, add details about requirements for packges running on all major platforms and added new section to package categories.

* 2019-01-22, add details to the guide for authors about the development stage at which to submit a package.

* 2018-12-21, inclusion of an explicity policy for conflict of interest (for reviewers and editors).

* 2018-12-18, added more guidance for editor on how to look for reviewers.

* 2018-12-04, onboarding was renamed Software Peer Review.

## place-holder 0.0.1

* Added a `NEWS.md` file to track changes to the book.

# Review template {#reviewtemplate}

```
```{r, child="templates/review.md"}
```
```



# Editor's template {#editortemplate}

```
```{r, child="templates/editor.md"}
```
```

# Review request template {#reviewrequesttemplate}

Editors may make use of the e-mail template below in recruiting reviewers.

```
```{r, child="templates/request.md"}
```
```
# Approval comment template {#approvaltemplate}

```
```{r, child="templates/approved.md"}
```
```

# NEWS template {#newstemplate}

```
```{r, child="templates/news.md"}
```
```
