# (APPENDIX) Appendix {-}

# NEWS {#booknews}

## 0.3.0

* 2020-02-10, add more guidance about secrets and package development in the security chapter.

* 2020-02-06, add package logo guidance (#217).

* 2020-02-06, add one CRAN gotcha: single quoting software names(#245, [`@aaronwolen`](https://github.com/aaronwolen))

* 2020-02-06, improve guidance regarding the replacement of "older" pkgdown website links and source (#241, [`@cboettig`](https://github.com/cboettig))

* 2020-02-06, rephrase the EiC role (#244).

* 2020-02-06, remove the recommendation to add rOpenSci footer (https://github.com/ropensci/software-review-meta/issues/79).

* 2020-02-06, remove the recommendation to add a review mention to DESCRIPTION but recommends mentioning the package version when reviewers are added as "rev" authors.

* 2020-01-30, slightly changes the advice on documentation re-use: add a con; mention `@includeRmd` and `@example`; correct the location of Rmd fragments (#230).

* 2020-01-30, add more guidance for the editor in charge of a dev guide release (#196, #205).

* 2020-01-22, add guidance in the editor guide about not transferred repositories.

* 2020-01-22, clarify forum guidance (for use cases and in general).

* 2020-01-22, mention an approach for pre-computing vignettes so that the pkgdown website might get build on rOpenSci docs server.

* 2020-01-22, document the use of mathjax with rotemplate ([`@Bisaloo`](https://github.com/Bisaloo), #199).

* 2020-01-20, add guidance for off-thread interaction and COIs ([`@noamross`](https://github.com/noamross), #197).

* 2020-01-20, add advice on specifying dependency minimum versions ([`@karthik`](https://github.com/karthik), [`@annakrystalli`](https://github.com/annakrystalli), #185).

* 2020-01-09, start using GitHub actions instead of Travis for deployment.

* -2019-12-11, add note in Documentation sub-section of Packaging Guide section about referencing the new R6 support in roxygen2 (ropensci/dev_guide#189)

* 2019-12-11, add new CRAN gotcha about having 'in R' or 'with R' in your package title ([`@bisaloo`](https://github.com/Bisaloo), ropensci/dev_guide#221)

* 2019-10-03, include in the approval template that maintainers should include link to the docs.ropensci.org/pkg site (ropensci/dev_guide#191)

* 2019-09-26, add instructions for handling editors to nominate packages for blog posts (ropensci/dev_guide#180)

* 2019-09-26, add chapter on changing package maintainers (ropensci/dev_guide#128) (ropensci/dev_guide#194)

* 2019-09-26, update Slack room to use for editors (ropensci/dev_guide#193)

* 2019-09-11, update instructions in README for rendering the book locally (ropensci/dev_guide#192)

* 2019-08-05, update JOSS submission instructions (ropensci/dev_guide#187)

* 2019-07-22, break "reproducibility" category in policies into component parts. (ropensci/software-review-meta#81)

* 2019-06-18, add link to rOpenSci community call "Security for R" to security chapter.

* 2019-06-17, fix formatting of Appendices B-D in the pdf version of the book (bug report by [`@IndrajeetPatil`](https://github.com/IndrajeetPatil), #179)

* 2019-06-17, add suggestion to use R Markdown hunks approach when the README and the vignette share content. (ropensci/dev_guide#161)

* 2019-06-17, add mention of central building of documentation websites.

* 2019-06-13, add explanations of CRAN checks. (ropensci/dev_guide#177)

* 2019-06-13, add mentions of the `rodev` helper functions where relevant.

* 2019-06-13, add recommendation about using `cat` for `str.*()` methods.  RStudio assumes that `str` uses `cat`, if not when loading an R object the `str` prints to the console in RStudio and doesn't show the correct object structure in the properties. ([`@mattfidler`] (https://github.com/mattfidler/) #178)

* 2019-06-12, add more details about git flow.

* 2019-06-12, remove recommendation about `roxygen2` dev version since the latest stable version has what is needed. ([`@bisaloo`](https://github.com/bisaloo/), #165)

* 2019-06-11, add mention of usethis functions for adding testing or vignette infrastructure in the part about dependencies in the package building guide.

* 2019-06-10, use the new URL for the dev guide, https://devguide.ropensci.org/

* 2019-05-27, add more info about the importance of the repo being recognized as a R package by linguist ([`@bisaloo`](https://github.com/bisaloo/), #172)

* 2019-05-22, update all links eligible to HTTPS and update links to the latest versions of Hadley Wickham and Jenny Bryan's books ([`@bisaloo`](https://github.com/bisaloo/), #167)

* 2019-05-15, add book release guidance for editors. (ropensci/dev_guide#152)

## 0.2.0

* 2019-05-23, add CRAN gotcha: in the Description field of your DESCRIPTION file, enclose URLs in angle brackets.

* 2019-05-13, add more content to the chapter about contributing.

* 2019-05-13, add more precise instructions about blog posts to approval template for editors.

* 2019-05-13, add policies allowing using either `<-` or `=` within a package as long as the whole package is consistent.

* 2019-05-13, add request for people to tell us if they use our standards/checklists when reviewing software elsewhere.

* 2019-04-29, add requirement and advice on testing packages using `devel` and `oldrel` R versions on Travis.

* 2019-04-23, add a sentence about why being generous with attributions and more info about ctb vs aut.

* 2019-04-23, add link to Daniel Nüst's notes about migration from XML to xml2.

* 2019-04-22, add use of rOpenSci forum to maintenance section.

* 2019-04-22, ask reviewer for consent to be added to DESCRIPTION in review template.

* 2019-04-22, use a darker blue for links (feedback by [`@kwstat
`](https://github.com/kwstat), #138).

* 2019-04-22, add book cover.

* 2019-04-08, improve formatting and link text in README ([`@katrinleinweber`](https://github.com/katrinleinweber), #137)

* 2019-03-25, add favicon ([`@wlandau`](https://github.com/wlandau), #136).

* 2019-03-21, improve Travis CI guidance, including link to examples. ([`@mpadge`](https://github.com/mpadge), #135)

* 2019-02-07, simplify code examples in Package Evolution section (maintenance_evolution.Rmd file) ([`@hadley`](https://github.com/hadley), #129).

* 2019-02-07, added a PDF file to export (request by [`@IndrajeetPatil`](https://github.com/IndrajeetPatil), #131).

## 0.1.5

* 2019-02-01, created a .zenodo.json to explicitly set editors as authors.

## First release 0.1.0

* 2019-01-23, add details about requirements for packages running on all major platforms and added new section to package categories.

* 2019-01-22, add details to the guide for authors about the development stage at which to submit a package.

* 2018-12-21, inclusion of an explicit policy for conflict of interest (for reviewers and editors).

* 2018-12-18, added more guidance for editor on how to look for reviewers.

* 2018-12-04, onboarding was renamed Software Peer Review.

## place-holder 0.0.1

* Added a `NEWS.md` file to track changes to the book.

# Review template {#reviewtemplate}

```markdown
```{r eval = !knitr::is_latex_output(), child="templates/review.md"}
```
```

```{r eval = knitr::is_latex_output(), child="templates/review.md"}

```



# Editor's template {#editortemplate}


```markdown
```{r eval = !knitr::is_latex_output(), child="templates/editor.md"}
```
```

```{r eval = knitr::is_latex_output(), child="templates/editor.md"}

```

# Review request template {#reviewrequesttemplate}

Editors may make use of the e-mail template below in recruiting reviewers.

```markdown
```{r eval = !knitr::is_latex_output(), child="templates/request.md"}
```
```

```{r eval = knitr::is_latex_output(), child="templates/request.md"}

```

# Approval comment template {#approvaltemplate}


```markdown
```{r eval = !knitr::is_latex_output(), child="templates/approved.md"}
```
```

```{r eval = knitr::is_latex_output(), child="templates/approved.md"}

```


# NEWS template {#newstemplate}


```markdown
```{r child="templates/news.md"}
```
```


# Book release guidance {#bookreleaseissue}


```markdown
```{r eval = !knitr::is_latex_output(), child="templates/book-release.md"}
```
```

```{r eval = knitr::is_latex_output(), child="templates/book-release.md"}

```

# How to set a redirect {#redirect}

Replace the content of the current website with

```html
<html>
<head>
<meta http-equiv="refresh" content="0;URL=https://docs.ropensci.org/<pkgname>/" />  
<script language="javascript">
  window.location.href = "https://docs.ropensci.org/<pkgname>"
</script>
</head>
</html>
```
    
