# (APPENDIX) Appendix {-}

# NEWS {#booknews}

## dev

* 2019-06-17, add mention of central building of documentation websites.

* 019-06-13, add explanations of CRAN checks.

* 2019-06-13, add mentions of the `rodev` helper functions where relevant.

* 2019-06-13, add recommendation about using `cat` for `str.*()` methods.  Rstudio assumes that `str` uses `cat`, if not when loading an R object the `str` prints to the console in Rstudio and doesn't show the correct object structure in the properties. ([`@mattfidler`] (https://github.com/mattfidler/) #178)

* 2019-06-12, remove recommendation about `roxygen2` dev version since the latest stable version has what is needed. ([`@bisaloo`](https://github.com/bisaloo/), #165)

* 2019-06-11, add mention of usethis functions for adding testing or vignette infrastructure in the part about dependencies in the package building guide.

* 2019-06-10, use the new URL for the dev guide, https://devguide.ropensci.org/

* 2019-05-27, add more info about the importance of the repo being recognised as a R package by linguist ([`@bisaloo`](https://github.com/bisaloo/), #172)

* 2019-05-22, update all links eligible to HTTPS and update links to the latest versions of Hadley Wickham and Jenny Bryan's books ([`@bisaloo`](https://github.com/bisaloo/), #167)

* 2019-05-15, add book release guidance for editors.

## 0.2.0

* 2019-05-23, add CRAN gotcha: in the Description field of your DESCRIPTION file, enclose URLs in angle brackets.

* 2019-05-13, add more content to the chapter about contributing.

* 2019-05-13, add more precise instructions about blog posts to approval template for editors.

* 2019-05-13, add policies allowing using either `<-` or `=` within a package as long as the whole package is consistent.

* 2019-05-13, add request for people to tell us if they use our standards/checklists when reviewing software elsewhere.

* 2019-04-29, add requirement and advice on testing packages using `devel` and `oldrel` R versions on Travis.

* 2019-04-23, add a sentence about why being generous with attributions and more info about ctb vs aut.

* 2019-04-23, add link to Daniel Nüst's notes about migration from XML to xml2.

* 2019-04-22, add use of rOpenSci forum to maintenance section.

* 2019-04-22, ask reviewer for consent to be added to DESCRIPTION in review template.

* 2019-04-22, use a darker blue for links (feedback by [`@kwstat
`](https://github.com/kwstat), #138).

* 2019-04-22, add book cover.

* 2019-04-08, improve formatting and link text in README ([`@katrinleinweber`](https://github.com/katrinleinweber), #137)

* 2019-03-25, add favicon ([`@wlandau`](https://github.com/wlandau), #136).

* 2019-03-21, improve Travis CI guidance, including link to examples. ([`@mpadge`](https://github.com/mpadge), #135)

* 2019-02-07, simplify code examples in Package Evolution section (maintenance_evolution.Rmd file) ([`@hadley`](https://github.com/hadley), #129).

* 2019-02-07, added a PDF file to export (request by [`@IndrajeetPatil`](https://github.com/IndrajeetPatil), #131).

## 0.1.5

* 2019-02-01, created a .zenodo.json to explicitly set editors as authors.

## First release 0.1.0

* 2019-01-23, add details about requirements for packages running on all major platforms and added new section to package categories.

* 2019-01-22, add details to the guide for authors about the development stage at which to submit a package.

* 2018-12-21, inclusion of an explicit policy for conflict of interest (for reviewers and editors).

* 2018-12-18, added more guidance for editor on how to look for reviewers.

* 2018-12-04, onboarding was renamed Software Peer Review.

## place-holder 0.0.1

* Added a `NEWS.md` file to track changes to the book.

# Review template {#reviewtemplate}

```
```{r, child="templates/review.md"}
```
```



# Editor's template {#editortemplate}

```
```{r, child="templates/editor.md"}
```
```

# Review request template {#reviewrequesttemplate}

Editors may make use of the e-mail template below in recruiting reviewers.

```
```{r, child="templates/request.md"}
```
```
# Approval comment template {#approvaltemplate}

```
```{r, child="templates/approved.md"}
```
```

# NEWS template {#newstemplate}

```
```{r, child="templates/news.md"}
```
```

# Book release guidance {#bookreleaseissue}

```
```{r, child="templates/book-release.md"}
```
```
